Size class small comparisons

### 2020-08-10 analysis/reports/manuscript_main.Rmd
reinstate direct size comparison

ggplot(filter(all_di, s0 > 2), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  geom_vline(xintercept = 95, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")

ggplot(all_di, aes(simpson_percentile)) + 
 geom_histogram(bins = 100) +
  geom_vline(xintercept = 5, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")

@@

overall_skew_results <- all_di %>%
  filter(s0 > 2) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(dat) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(dat) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

@@

overall_skew_results2 <- all_di %>%
  mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
  filter(s0 > 2) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(fia_yn) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results2 <- all_di %>%
   mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(fia_yn) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

@@

ggplot(all_di, aes(x = log_nparts, y= skew_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100)

ggplot(all_di, aes(x = log_nparts, y= simpson_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100)

>>>>

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  geom_vline(xintercept = 95, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")

ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
 geom_histogram(bins = 100) +
  geom_vline(xintercept = 5, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")

@@

overall_skew_results <- all_di %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(dat) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  filter(simpson_unique > 20) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(dat) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

@@

overall_skew_results2 <- all_di %>%
  mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(fia_yn) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results2 <- all_di %>%
  filter(simpson_unique > 20) %>%
   mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(fia_yn) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

@@

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100)

ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100)

### 2020-08-10 analysis/reports/nunique.Rmd
reinstate direct size comparison

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         !singletons,
         s0 > 1,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
```

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         !singletons,
         s0 > 1,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))

ggplot(filter(all_di, s0> 2), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di, s0> 2, skew_unique > 100), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y")

```

### 2020-08-10 analysis/reports/smallness.Rmd
reinstate direct size comparison

ggplot(filter(all_di, s0 > 2), aes(skew_percentile_excl)) +
  geom_histogram(bins = 20) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di), aes(simpson_percentile)) +
  geom_histogram(bins = 20) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")
```

@@

ggplot(small_di, aes(log_nparts)) +
  geom_histogram(bins = 30) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")

@@

ggplot(sub_di, aes(skew_percentile_excl)) +
  geom_histogram()+
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")

ggplot(sub_di, aes(simpson_percentile)) +
  geom_histogram()+
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")

sub_di %>%
  filter(s0 > 2) %>%
  group_by(fia_yn) %>%
  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
            prop_even_low = mean(simpson_percentile < 5),
            nsites = dplyr::n())

>>>>

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
  geom_histogram(bins = 20) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) +
  geom_histogram(bins = 20) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")
```

@@

ggplot(filter(small_di), aes(log_nparts)) +
  geom_histogram(bins = 30) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")

@@

ggplot(filter(sub_di, skew_unique > 20), aes(skew_percentile_excl)) +
  geom_histogram()+
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")

ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_percentile)) +
  geom_histogram()+
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")
# 
# 
# 
# ggplot(filter(sub_di), aes(skew_percentile_excl)) +
#   geom_histogram()+
#   theme_bw() +
#   facet_wrap(vars(fia_yn), scales = "free_y")
# 
# ggplot(filter(sub_di), aes(simpson_percentile)) +
#   geom_histogram()+
#   theme_bw() +
#   facet_wrap(vars(fia_yn), scales = "free_y")

sub_di %>%
  filter(s0 > 2) %>%
  group_by_all %>%
  mutate(skew_percentile_excl = ifelse(skew_unique >= 20, skew_percentile_excl, NA),
         simpson_percentile = ifelse(simpson_unique >= 20, simpson_percentile, NA)) %>%
  ungroup() %>%
  group_by(fia_yn) %>%
  summarize(prop_skew_high = mean(skew_percentile_excl > 95, na.rm = T),
            prop_even_low = mean(simpson_percentile < 5, na.rm = T),
            nsites_skew = sum(!is.na(skew_percentile_excl)),
            nsites_even = sum(!is.na(simpson_percentile)))

sum(sub_di$skew_unique < 20)
sum(sub_di$simpson_unique < 20)
```
